Simulate

### 2023-07-05 Code/Simulation.Rmd
Something from meeting

```{}

If we want to pick the barrier based on the reaction time a barrier of 0.08905, 1 in every 1001.603
If we want to pick the barrier based on the reaction time a barrier of 0.089, 1 in every 1012.248
If we want to pick the barrier based on the reaction time a barrier of 0.089057, 1 in every 999.9
If we want to pick the barrier based on the reaction time a barrier of 0.089056, 1 in every 1000.2
```

@@

```{r}
set.seed(1)
simulation(old_finals_year_gamma_log, old_finals_one_gamma_log, 0.0001)
simulation(men_finals_year_gamma_log, men_finals_one_gamma_log, 0.0001)
simulation(old_pooled_year_gamma_log, old_pooled_one_gamma_log, 0.0001)
simulation(men_pooled_year_gamma_log, men_pooled_one_gamma_log, 0.0001)
```

>>>>

```{}
If we want to pick the barrier based on the reaction time a barrier of 0.08905, 1 in every 1001.603
If we want to pick the barrier based on the reaction time a barrier of 0.089, 1 in every 1012.248
If we want to pick the barrier based on the reaction time a barrier of 0.089057, 1 in every 999.9
If we want to pick the barrier based on the reaction time a barrier of 0.089056, 1 in every 1000.2
```

@@

Change the name
```{r}
set.seed(1)
simulation(old_finals_year_gamma_log, old_finals_one_gamma_log, 0.0001)
simulation(men_finals_year_gamma_log, men_finals_one_gamma_log, 0.0001)
simulation(old_pooled_year_gamma_log, old_pooled_one_gamma_log, 0.0001)
simulation(men_pooled_year_gamma_log, men_pooled_one_gamma_log, 0.0001)
```
